Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-04-13 finalReportPres.tex
Update final report presentation and lab notebook
Update finalReportPres.tex
I added to the Modeling using Neural Networks slide
Updated Final Presentation

\subject{Mobile Robot Localization}
% This is only inserted into the PDF information catalog. Can be left
% out.

@@

\begin{frame}{Introduction}{Problem Statement}
  \begin{block}{Problem Statement}
    \begin{Large}
    		Model autonomous vehicle subsystems for a Lexus platform
    \end{Large}
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{Large}
    		Use neural network modeling techniques to develop models
    \end{Large}
  \end{block}
\end{frame}

@@

%\begin{frame}{Introduction}{Previous Work}
%  \begin{block}{Existing Solution}
%        Mobile application platform interface with ultrasound and radio transmission technology~\cite{Sales2016-CompaRob}
%  \end{block}
%    % \begin{figure}[b]
%    %     \centering
%    %     \includegraphics[width=0.4\textwidth]{figs/img/CompaRob}
%    %     \caption{CompaRob}
%    %     %\label{fig:sysBlockDiag}
%    % \end{figure}
%\end{frame}
%
%%----------------------------------
%
%\begin{frame}{Introduction}{Previous Work}
%  \begin{block}{Existing Solution}
%        Gated Recurrent Unit (GRU) network with LiDAR sensor and camera to map the customer~\cite{islam_lam_fukuda_kobayashi_kuno_2019}
%  \end{block}
%    % \begin{figure}[b]
%    %     \centering
%    %     \includegraphics[width=0.38\textwidth]{figs/img/ShoppingSuportRobot}
%    %     \caption{Shopping Support Robot}
%    %     %\label{fig:sysBlockDiag}
%    % \end{figure}
%\end{frame}

@@

\begin{frame}{Literature Review}{}
	\begin{block}{Existing Solutions}
 	\begin{itemize}
        \item Use of System Identification Toolbox in MATLAB to create models from data~\cite{Adnan2010}
	 \begin{itemize}
     \tiny
		    		\item Offers a variety of model choices
				\item Needs a large amount of raw data to produce an accurate model
	\end{itemize}
	\item Third order ARMAX model creates models using traditional methods of analysis~\cite{Li1999}
	 \begin{itemize}
     \tiny
		    		\item Allows the use of traditional analysis methods to create a model 
				\item More room for error during calculations
	\end{itemize}
	\item Steer-By-Wire method as a system model~\cite{Saruchi2015}
	 \begin{itemize}
     \tiny
		    		\item Can model systems with small non-linearities 
				\item Mechanical components replaced by electrical components 
	\end{itemize}
	\item Authors in~\cite{Hussain2011} illustrate identification of multiple-input single-output model for maximum power point tracking of photovoltaic system.  
	\begin{itemize}
    \tiny
		\item Fourth order ARX model ended up giving the best fit
	\end{itemize}
\end{itemize}
  \end{block}
\end{frame}
%---------------------------
\section{System Identification Preliminaries}

@@

\begin{frame}{System Identification Preliminaries}{Examples}
  \begin{block}{}
    \begin{LARGE}

    \end{LARGE}
  \end{block}
  \begin{block}{}
    \begin{LARGE}

    \end{LARGE}
  \end{block}
\end{frame}
%-------------------------
\section{System Architecture}

@@

\begin{frame}{System Architecture}{Subsystems}
	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/shiftModelArchitecture}\quad%
	\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Shift System \item 		Speed Control System \item Speed System \end{enumerate} \end{minipage}\\[1em]
	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedControlModelArchitecture}\quad%
	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedModelArchitecture}
\end{frame}
%---------------------------
\section{System Modeling using Neural Networks}

\begin{frame}{Modeling using Neural Networks}{}

\end{frame}
%-------------------------
\section{Modeling Vehicle Subsystems}

\begin{frame}{Modeling Vehicle Subsystems}{}

@@

\begin{frame}{Transfer Function Modeling}{Steering System}
	\begin{block}
 \begin{itemize}
	\item Best fit percentage of the by-wire steering estimated model is 85.54
	\item Best fit percentage of the manual steering estimated model is 90.27
 \end{itemize}
 \begin{figure}
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
        \caption{Output of Estimated By-Wire System Model}
        \label{fig:byWireSteerModel}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
        \caption{Output of Estimated Manual System Model}
        \label{fig:manualSteerModel}
    \end{minipage}
\end{figure}
  \end{block}
\end{frame}

\begin{frame}{Transfer Function Modeling}{Acceleration System}
	\begin{block}
 \begin{itemize}
	\item Best fit percentage of the by-wire acceleration estimated model is 97.69
	\item Best fit percentage of the manual acceleration estimated model is 98.3
 \end{itemize}
 \begin{figure}
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
        \caption{Output of Estimated By-Wire System Model}
        \label{fig:byWireAccelModel}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
        \caption{Output of Estimated Manual System Model}
        \label{fig:manualAccelModel}
    \end{minipage}
\end{figure}
  \end{block}
\end{frame}

\begin{frame}{Transfer Function Modeling}{Brake System}

@@

\begin{frame}{Neural Network Modeling}{Steering System}
	\begin{block}
  		\begin{figure}[H]
  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringSimulinkBlock.jpg}\quad%
			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
			\item Only a few samples are just outside of the accuracy requirements
			\item Transfer function model did not meet the accuracy requirements
			\end{itemize} \end{minipage}\\[1em]
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput.jpg}\quad%
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput2.jpg}
  		\end{figure}
	\end{block}
\end{frame}

\begin{frame}{Neural Network Modeling}{Acceleration System}
	\begin{block}
  		\begin{figure}[H]
  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelerationSimulinkBlock.jpg}\quad%
			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
			\item All samples within 2\% of the actual output
			\item Transfer function model did not have the same accuracy bounds
			\item Fewer concerns about connections in Simulink
			\end{itemize} \end{minipage}\\[1em]
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput.jpg}\quad%
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput2.jpg}
  		\end{figure}
	\end{block}
\end{frame}

\begin{frame}{Neural Network Modeling}{Brake System}
	\begin{block}
\begin{figure}[H]
  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/newBrakeSimulinkBlock.jpg}\quad%
			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
			\item With this model, the error is kept below 5\%
			\item Able to easily track model performance
			\item Provides better results than the transfer function model
			\end{itemize} \end{minipage}\\[1em]
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFig.jpg}\quad%
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFigLog2Test.jpg}
  		\end{figure}

>>>>

\subject{Plant Modeling for Autonomous Vehicle}
% This is only inserted into the PDF information catalog. Can be left
% out.

@@

\begin{frame}{Introduction}{Problem Statement}
  \begin{block}{Problem Statement}
    \begin{Large}
    		Model autonomous vehicle subsystems for a Lexus platform
    \end{Large}
  \end{block}
  \pause
  \begin{block}{Proposed Solution}
    \begin{Large}
    		Use neural network modeling techniques to develop plant models
    \end{Large}
  \end{block}
\end{frame}

@@

@@

\begin{frame}{Literature Review}{}
	\begin{block}{Existing Solutions}
 	\begin{itemize}
        \item Use of System Identification Toolbox in MATLAB to create models from data~\cite{Adnan2010}
	 \begin{itemize}
     \tiny
		    		\item Offers a variety of model choices
				\item Needs a large amount of raw data to produce an accurate model
	\end{itemize}
	\item Third order ARMAX model creates models using traditional methods of analysis~\cite{Li1999}
	 \begin{itemize}
     \tiny
		    		\item Allows the use of traditional analysis methods to create a model 
				\item More room for error during calculations
	\end{itemize}
	\item Steer-By-Wire method as a system model~\cite{Saruchi2015}
	 \begin{itemize}
     \tiny
		    		\item Can model systems with small non-linearities 
				\item Mechanical components replaced by electrical components 
	\end{itemize}
	\item Authors in~\cite{Hussain2011} illustrate identification of multiple-input single-output model for maximum power point tracking of photovoltaic system.  
	\begin{itemize}
    \tiny
		\item Fourth order ARX model ended up giving the best fit
	\end{itemize}
\end{itemize}
  \end{block}
\end{frame}

%---------------------------
\section{System Identification Preliminaries}

@@

%-------------------------
\section{System Architecture}

@@

\begin{frame}{System Architecture}{Subsystems}
	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/shiftModelArchitecture}\quad%
	\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth} \begin{enumerate} \item Shift System \item 		Speed Control System \item Speed System \end{enumerate} \end{minipage}\\[1em]
	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedControlModelArchitecture}\quad%
	\centering \includegraphics[width=.45\linewidth]{figs/inkscape/speedModelArchitecture}
\end{frame}

%---------------------------
\section{System Modeling using Neural Networks}

\begin{frame}{Modeling using Neural Networks}{}
	\begin{block}{}
 \begin{itemize}
        \item Used MATLAB's Neural Network Time Series App 
        \item All models generated using the Bayesian Regularization Algorithm 
        \item Models trained using collected log data 
\end{itemize}
  \end{block}
\end{frame}

%-------------------------
\section{Modeling Vehicle Subsystems}

@@

\begin{frame}{Validation and Testing}{Validation Setup}

@@

\begin{frame}{Transfer Function Modeling}{Steering System}
	\begin{block}{}
 \begin{itemize}
	\item Best fit percentage of the by-wire steering estimated model is 85.54
	\item Best fit percentage of the manual steering estimated model is 90.27
 \end{itemize}
 \begin{figure}
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
        \caption{Output of Estimated By-Wire System Model}
        \label{fig:byWireSteerModel}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
        \caption{Output of Estimated Manual System Model}
        \label{fig:manualSteerModel}
    \end{minipage}
\end{figure}
  \end{block}
\end{frame}

\begin{frame}{Transfer Function Modeling}{Acceleration System}
	\begin{block}{}
 \begin{itemize}
	\item Best fit percentage of the by-wire acceleration estimated model is 97.69
	\item Best fit percentage of the manual acceleration estimated model is 98.3
 \end{itemize}
 \begin{figure}
    \centering
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/byWireAccelArxModel} % first figure itself
        \caption{Output of Estimated By-Wire System Model}
        \label{fig:byWireAccelModel}
    \end{minipage}\hfill
    \begin{minipage}{0.45\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{figs/img/manualAccelTransferFunctionModel} % second figure itself
        \caption{Output of Estimated Manual System Model}
        \label{fig:manualAccelModel}
    \end{minipage}
\end{figure}
  \end{block}
\end{frame}

\begin{frame}{Transfer Function Modeling}{Brake System}
\begin{block}{}
 \begin{itemize}
	\item Only manual models were considered 
	\item There were no transfer function models that could satisfy both the best fit and error requirements 
 \end{itemize}
% \begin{figure}
%    \centering
%    \begin{minipage}{0.45\textwidth}
%        \centering
%        \includegraphics[width=0.6\textwidth]{figs/img/byWireSteeringTransferFunctionModel} % first figure itself
%        \caption{Output of Estimated By-Wire System Model}
%        \label{fig:byWireSteerModel}
%    \end{minipage}\hfill
%    \begin{minipage}{0.45\textwidth}
%        \centering
%        \includegraphics[width=0.6\textwidth]{figs/img/manualSteeringTransferFunctionModel} % second figure itself
%        \caption{Output of Estimated Manual System Model}
%        \label{fig:manualSteerModel}
%    \end{minipage}
%\end{figure}
  \end{block}
\end{frame}

\begin{frame}{Neural Network Modeling}{Steering System}
	\begin{block}{}
  		\begin{figure}[H]
  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringSimulinkBlock.jpg}\quad%
			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
			\item Only a few samples are just outside of the accuracy requirements
			\item Transfer function model did not meet the accuracy requirements
			\end{itemize} \end{minipage}\\[1em]
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput.jpg}\quad%
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput2.jpg}
  		\end{figure}
	\end{block}
\end{frame}

\begin{frame}{Neural Network Modeling}{Acceleration System}
	\begin{block}{}
  		\begin{figure}[H]
  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelerationSimulinkBlock.jpg}\quad%
			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
			\item All samples within 2\% of the actual output
			\item Transfer function model did not have the same accuracy bounds
			\item Fewer concerns about connections in Simulink
			\end{itemize} \end{minipage}\\[1em]
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput.jpg}\quad%
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput2.jpg}
  		\end{figure}
	\end{block}
\end{frame}

\begin{frame}{Neural Network Modeling}{Brake System}
	\begin{block}{}
\begin{figure}[H]
  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/newBrakeSimulinkBlock.jpg}\quad%
			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
			\item With this model, the error is kept below 5\%
			\item Able to easily track model performance
			\item Provides better results than the transfer function model
			\end{itemize} \end{minipage}\\[1em]
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFig.jpg}\quad%
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFigLog2Test.jpg}
  		\end{figure}
